Map/Reduce for the common man

### 2010-02-16 doc/slides.tex
*** empty log message ***

>>>>

\begin{frame}\frametitle{Sequential}
the sequential implementation is obvious

  \begin{ocaml}
let map ~f l = List.map f l

let map_local_reduce ~map ~reduce acc l =
  List.fold_left (fun a x -> reduce a (map x)) acc l

let map_remote_reduce = map_local_reduce

let map_reduce_ac = map_local_reduce

let map_reduce_a = map_local_reduce
  \end{ocaml}
\end{frame}

\begin{frame}\frametitle{Cores / Network}

  \texttt{Cores} and \texttt{Network} share a main routine

  abstract notions of \emph{workers} and \emph{tasks}; we can
  \begin{enumerate}
  \item assign a task to a worker
  \item wait for a completed job, which may generate new tasks
  \end{enumerate}

  so the main loop is
  \begin{lightblue-tt}
    while pending tasks || pending jobs
      while pending tasks && idle workers
        assign any task to any idle worker
      wait for any completed job
        push new pending tasks
  \end{lightblue-tt}
